Vragenlijst thesis evaluatie

### 2015-06-28 doc/template/chap-10.tex
Nog verdere aanvullingen

The organisation of this paper is the following.  In chapter \ref{Chapter1:Intro.Game.Theory}  a brief introduction to cyber security and game theory is introduced to get familiar with the kind of threats that are in the scope of this work and the game theoretic concepts that will be further used in the paper. In the same chapter the FlipIt framework is summarized with its most important conclusions. The chapter concludes with related work on FlipIt and further clarifies the contributions of this paper compared to existing work. 
Chapter \ref{chapter2:FlipIt with virus propagation} , first introduces the adaptations made to the original FlipIt model to model a FlipIt game with virus propagation. Subsequently formulas are derived to model a FlipIt game with a virus propagation for the specific case where players play a periodic strategy with a random phase. \\
In Chapter \ref{chapter:Nash} the formules are further analysed to determine if there is a nash equilibrium. \todo{aanpassen naar chapter met nash equilibria}
In order to provide a clear perspective on delays, chapter \ref{chapter4: Virus propagation} gives an overview of the various ways in which a virus can propagate. It presents a method to calculate the speed of the propagation of a virus in a network and how this network can be established to reduce the spreading of a virus.
Finally chapter \ref{chapter5:conclusion} , we discusses the main results and provides directions for further research.

>>>>

The organisation of this paper is the following.  An introduction to cyber security and game theory is given in chapter \ref{Chapter1:Intro.Game.Theory} to get familiar with the kind of threats that are in the scope of this work and the game theoretic concepts that will be further used in the paper. In the same chapter the FlipIt framework is summarized with its most important conclusions. The chapter concludes with related work on FlipIt and further clarifies the contributions of this paper compared to existing work. 
Chapter \ref{chapter2:FlipIt with virus propagation} , first introduces the adaptations made to the original FlipIt model to model a FlipIt game with virus propagation. Subsequently formulas are derived to model a FlipIt game with a virus propagation for the specific case where players play a periodic strategy with a random phase. \\
In Chapter \ref{chapter:Nash} the formulas are further analysed to determine if there is a nash equilibrium. 
In order to provide a clear perspective on delays, chapter \ref{chapter4: Worm propagation} gives an overview of the various methods of propagation and worm propagation models. It presents a method to calculate the speed of the propagation of a worm in a network independent of the topology of the network.
Finally chapter \ref{chapter5:conclusion} , we discusses the main results and provides directions for further research.

### 2015-06-28 doc/template/chap-4.tex
Nog verdere aanvullingen

The  spreading of malware has already been extensively researched. Because of the many different types of propagation it is hard to defined a single model that can model all of them. Modelling the spread of malware depends on two key factors: the method used for the propagation and the graph where the malware will spread itself. \\
Viruses and worms are the types of malware that are the most researched. Since the spreading of viruses requires human interaction, their propagation delay is depending on (hard to predict) human behaviour. Worms on the other hand, spread without human intervention, and are their propagation is therefore easier to model. Since the purpose of this chapter is only to illustrate how a delay can be calculated, we will limit the presentation to propagation models of worms . Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} that presents models to determine the time a worm needs to infect a sufficient number of nodes. These results can be used for the completion of parameter \textit{d}. Finally, in section \ref{eigenmatrixmethode},  we introduce an easy method to calculate the delay of the propagation of a worm.  Different kind of graphs to model a computer network are introduced.

@@

SI, SIR, SIS assume $\beta$ to be constant.

Continious-time model
\subsubsection{Simple Epidemic model}
%Codered paper gebruikt voor model
A Simple epidemic model is SI model. Nodes in the network can be either susceptible or infected.
Once a node is infected it will stay infected. 
The simple epidemic model is considered to be of a fixed size. The model for a fixed population is as follows:
\begin{equation}
\dfrac{d I(t)}{dt} = \beta I(t)[N-I(t)]
\end{equation} 
where I(t) is the number of infected hosts at time t; $\beta$ is the propagation rate; and N is the number of nodes in the network. In the beginning, $t=0$, I(0) hosts are infected. All the other nodes, $N - I(0)$, in the network are susceptible. 
The solution of this equation is the following logistic curve:
\begin{equation}
I = \dfrac{e^{\beta(t-T)}}{1+e^{\beta(t-T)}}
\end{equation}
where T is a time parameter representing the point of maximum increase in the
growth.\\

@@

Figuur \ref{SEMmodel} laat het SEM model zien.
This Simple epidemic model has been used in various papers \cite{OwnInternetSI} \cite{CodeRed} to model random scanning worm such as Code Red and Slammer. \\
For our paper we have to approximate the propagation speed en Infect gelijkstellen aan het aantal genoeg nodes die geinfecteerd moeten zijn door de APT om de controle te hebben. Dan weten we hoelang het duurt. In het begin zullen er ook geen geinfecteerde hosts zijn, dus de vergelijking kan opgelost worden.\\
Er wordt geen rekening gehouden met de topology ? nog uitzoeken.
\subsubsection{Kermack-Mckendrick model: SIR}
In the Kermack-Mckendrick model, also known as SIR model, nodes can have three states: susceptible, infected or removed. Once a node of the network has been recovered from a worm, the node will stay in the removed mode and never becomes infected again. These nodes are not able to infect other nodes and can no longer be infected. \\
Let I(t) be the number of infectious hosts at time \textit{t}, R(t) be the number of removed hosts at time \textit{t} and J(t) is the number of infected hosts by time \textit{i}, regardless the fact that a node can be in a removed state.
\begin{equation}
J(t) = I(t) + R(t).
\end{equation} 
The Kermack-McKendrick model can be represented as follows:
\begin{equation}
\begin{Bmatrix} \dfrac{d J(t)}{dt} = \beta J(t) \big[N- J(t) \\
\dfrac{d R(t)}{dt} = \gamma I(t) \\
J(t) = I(t) + R(t) = N - S(t)
 \end{Bmatrix}
\end{equation}
Parameter $\beta$ is again the rate of infection and $\gamma$ is the rate of removal of infected hosts. S(T) is the number of susceptible hosts at time t.
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{Images/KMmodel.png}
\caption{KM Model. The x-coordinate is the propagation time and the y-coordinate is the infected percentage of the whole network. Original image from \cite{OnWorms2005survey}. $N=10000, \beta = 1/10000000$.}
\label{KMmodel}
\end{figure}

>>>>

The  spreading of malware has already been extensively researched. Because of the many different types of propagation it is hard to defined a single model that can model all of them. Modelling the spread of malware depends on two key factors: the method used for the propagation and the graph where the malware will spread itself. \\
Viruses and worms are the types of malware that are the most researched. Since the spreading of viruses requires human interaction, their propagation delay is depending on (hard to predict) human behaviour. Worms on the other hand, spread without human intervention, and are their propagation is therefore easier to model. Since the purpose of this chapter is only to illustrate how a delay can be calculated, we will limit the presentation to propagation models of worms. \\

The overview of this chapter will be as follow: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} that presents models to determine the time a worm needs to infect a sufficient number of nodes. These results can be used for the completion of parameter \textit{d}. Finally, in section \ref{eigenmatrixmethode},  we introduce an easy method to calculate the delay of the propagation of a worm.  Different kind of graphs to model a computer network are introduced.

@@

The following papers cover the most common propagation models: \cite{wang2014modeling}, \cite{OnWorms2005survey}, \cite{xiang2009propagation} and \cite{serazzi2004computer}.
In this section we only list the models that are the most interesting from the perspective of calculating the delay.
SI, SIR, SIS assume $\beta$ to be constant.

Tree model figure \ref{tree}

\begin{figure}
\centering
\includegraphics[scale=0.5]{Images/TreeModel.png} 
\caption{Taxonomy of worm modeling. Original tree from \cite{wang2014modeling}}.
\label{ShapeUp}
\end{figure}
Continious-time model
\subsubsection{Simple Epidemic model}
%Codered paper gebruikt voor model
A Simple epidemic model is SI model. Nodes in the network can be either susceptible or infected.
Once a node is infected it will stay infected. 
The simple epidemic model is considered to be of a fixed size. The model for a fixed population is as follows:
\begin{equation}
\dfrac{d I(t)}{dt} = \beta I(t)[N-I(t)]
\end{equation} 
where I(t) is the number of infected hosts at time t; $\beta$ is the propagation rate; and N is the number of nodes in the network. In the beginning, $t=0$, I(0) hosts are infected. All the other nodes, $N - I(0)$, in the network are susceptible. 
The solution of this equation is the following logistic curve:
\begin{equation}
I = \dfrac{e^{\beta(t-T)}}{1+e^{\beta(t-T)}}
\end{equation}
where T is a time parameter representing the point of maximum increase in the
growth.\\

@@

Figuur \ref{SEMmodel} laat het SEM model zien.
This Simple epidemic model has been used in various papers \cite{OwnInternetSI}, \cite{CodeRed} to model random scanning worm such as Code Red and Slammer. \\
For our paper we have to approximate the propagation speed en Infect gelijkstellen aan het aantal genoeg nodes die geinfecteerd moeten zijn door de APT om de controle te hebben. Dan weten we hoelang het duurt. In het begin zullen er ook geen geinfecteerde hosts zijn, dus de vergelijking kan opgelost worden.\\
Er wordt geen rekening gehouden met de topology ? nog uitzoeken.
\subsubsection{Kermack-Mckendrick model: SIR}
In the Kermack-Mckendrick model, also known as SIR model, nodes can have three states: susceptible, infected or removed. Once a node of the network has been recovered from a worm, the node will stay in the removed mode and never becomes infected again. These nodes are not able to infect other nodes and can no longer be infected. \\
Let I(t) be the number of infectious hosts at time \textit{t}, R(t) be the number of removed hosts at time \textit{t} and J(t) is the number of infected hosts by time \textit{i}, regardless the fact that a node can be in a removed state.
\begin{equation}
J(t) = I(t) + R(t).
\end{equation} 
The Kermack-McKendrick model can be represented as follows:
\begin{equation}
\begin{Bmatrix} \dfrac{d J(t)}{dt} = \beta J(t) \big[N- J(t) \\
\dfrac{d R(t)}{dt} = \gamma I(t) \\
J(t) = I(t) + R(t) = N - S(t)
 \end{Bmatrix}
\end{equation}
Parameter $\beta$ is again the rate of infection and $\gamma$ is the rate of removal of infected hosts. S(T) is the number of susceptible hosts at time t.
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.5]{Images/KMmodel.png}
\caption{KM Model. The x-coordinate is the propagation time and the y-coordinate is the infected percentage of the whole network. Original image from \cite{OnWorms2005survey}. $N=10000, \beta = 1/10000000$.}
\label{KMmodel}
\end{figure}

### 2015-06-28 doc/template/nash.tex
figuren toegevoegd
versie voor mama
alpha -> delta
nash aanvullen
Nog verdere aanvullingen

\section{Nash Equilibria}
-- rechtstreeks uit FlipIt paper --\\
As a second step, we are interested in finding Nash equilibria, points
for which neither player will increase his benefit by changing his rate of play. More
formally, a Nash equilibrium for the periodic game is a point $(\alpha_{0}^{*},\alpha_{1}^{*})$ such that
the defender's benefit $\beta_{0}(\alpha_{0},\alpha_{1}^{*}) $is maximized at $\alpha_{0}= \alpha_{0}^{*}$ and the attacker's benefit
$\beta_{1}(\alpha_{0}^{*},\alpha_{1}) $ is maximized at $\alpha_{1}= \alpha_{1}^{*}$ .
To begin with, some useful notation. We denote by opt0($\alpha_{1}$) the set of values (rates
of play $\alpha_{0}$) that optimize the benefit of the defender for a fixed rate of play $\alpha_{1}$ of the
attacker. Similarly, we denote by opt1($\alpha_{0}$) the set of values (rates of play $\alpha_{1}$) that optimize
the benefit of the attacker for a fixed rate of play $\alpha_{0}$ of the defender. The following
theorem specifies Nash equilibria for the periodic game and is proven in Appendix A. \\
\begin{figure}[hbtp]
\caption{This figure shows the three subcategories of each case. 'A' stands for Case 2.A: $\delta_{D} \geq d+\delta_{A} \geq \delta_{A}$ and 'B' stands for Case 2.B: $d+\delta_{A} \geq \delta_{D} \geq  \delta_{A} $ }
\centering
\includegraphics[scale=0.4]{Images/bestresp.png}
\label{grafiekbestr}
\end{figure}

@@

Nash equilibria are points with the property that neither player benefits by deviating in isolation form equilibrium. We can compute Nash Equilibria for the periodic game as an intersection points of curvest opt0 and opt1. To determine opt0(a0) we need to compute the derivative of  $\beta_{0}(\alpha_{0},\alpha_{1}) $ for a fixed $\alpha_{1}$. We consider two cases:\\

\subsection*{Case 1: $\delta_{D} \leq \delta_{A} $}
The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\beta_{D}(\alpha_{D},\alpha_{A}) = 1 - \dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{D}}{\delta_{D}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}} + \dfrac{d}{\delta_{A}}
\end{equation*}
If we take the partial derivative for a fixed $\delta_{1}$ we get the following result:
\begin{equation*}\label{formdelta}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = - \dfrac{1}{2\delta_{A}} + \dfrac{k_{D}}{\delta_{D}^{2}} + \dfrac{d^{2}}{2\delta_{D}^{2}\delta_{A}}
\end{equation*}

The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{D} = \sqrt{2\delta_{A}k_{D} + d^{2}}
\end{equation*}

This leads to the following deduction: The function increases on $[0, \sqrt{2\delta_{A}k_{D} + d^{2}}]$ and is decreasing on $[\sqrt{2\delta_{A}k_{D} + d^{2}}, \infty]$ So we got a maximum on $\delta_{D} = min \{ \delta_{A}, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $. The minimum of the two values is needed because $\delta_{D}$ cannot be bigger than $\delta_{A}$. \\
~~\\

@@

The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\dfrac{t \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}}
\end{equation*}

The derivative of the above formula for a fixed $\delta_{A}$ results in the following:
\begin{equation*}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = -\dfrac{\delta_{A}}{2\delta_{D}^{2}} - \dfrac{d}{\delta_{D}^{2}} + \dfrac{k_{D}}{\delta_{D}^{2}}
\end{equation*}
The obtain the stationary points the first derivative is set equal to zero and the roots of the resulting equation are found:
\begin{equation*}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{A} = 2(k_{D}-d) = dk_{D} - 2d
\end{equation*}

This leads to the following deduction:
\begin{description}
\item If $k_{D} \leq d$ 
\begin{description}
\item decreasing $ \delta_{A} < 2(k_{D} -d)$
\item increasing  $\delta_{A} > 2(k_{D} -d)$ 
\end{description}
\item If $k_{D} > d$ 
\begin{description}
\item increasing $ \delta_{A} < 2(k_{D} -d)$
\item decreasing  $\delta_{A} > 2(k_{D} -d)$ 
\end{description}
\end{description}
~~\\

@@

The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\dfrac{\beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} - \dfrac{(d-(\delta_{D} - \delta_{A}))^{2}}{d\delta_{D}\delta_{A}}
\end{equation*}

The derivative of the above formula for a fixed $\delta_{A}$ results in the following:
\begin{equation*}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =  - \dfrac{1}{2\delta_{D}} + \dfrac{k_{D}}{\delta_{D}^{2}} + \dfrac{d^{2}}{2\delta_{D}^{2}\delta_{A}}
\end{equation*}

@@

\begin{equation*}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{D} = \sqrt{2\delta_{A}k_{D} + d^{2}}
\end{equation*}

This leads to the following deduction: The function increases on $[0, \sqrt{2\delta_{A}k_{D} + d^{2}}]$ and is decreasing on $[\sqrt{2\delta_{A}k_{D} + d^{2}}, \infty]$ So we got a maximum on $\delta_{D} = minimum \{ \delta_{A}, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $ \\

@@

The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =\dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} - \dfrac{d}{\delta_{A}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =0 ~~~~~~ =>~~~~~~ 2k_{A} = \dfrac{(\delta_{D}-d)^{2}}{\delta_{D}}
\end{equation*}

@@

\subsection*{Case 2.A: $\delta_{D} \geq d+\delta_{A} \geq \delta_{A} $ }
The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =1- \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{k_{A}}{\delta_{A}} - \dfrac{d}{\delta_{D}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = \dfrac{-1}{2\delta_{D}} + \dfrac{k_{A}}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{A} = \sqrt{2\delta_{D}k_{A}}
\end{equation*}
it follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing on $[0,\sqrt{2k_{A}\delta_{D}}]$ and decreasing on $[\sqrt{2k_{A}\delta_{D}}, \infty]$ and thus has a maximum on $\delta_{A} = maximum \{\delta_{D}, \sqrt{2k_{A}\delta_{D}} \} $. The maximum between $\delta_{D}$ and $ \sqrt{2k_{A}\delta_{D}}$ is needed because $\delta_{A} $ cannot exceed $\delta_{D}$ in this case. \\

@@

The benefit formula obtained previously for this case is as follows: 
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) = 1 - \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{(d-(\delta_{D}-\delta_{A})^{2}}{2\delta_{D}\delta_{A}} 
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\alpha_{D},\alpha_{A})}{\partial \alpha_{D}} =0 ~~~~~~ =>~~~~~~ 2k_{A} = \dfrac{(\delta_{D}-d)^{2}}{\delta_{D}}
\end{equation*}

@@

>>>>

\section{Nash Equilibria}
-- rechtstreeks uit FlipIt paper --\\
As a second step, we are interested in finding Nash equilibria, points
for which neither player will increase his benefit by changing his rate of play. More
formally, a Nash equilibrium for the periodic game is a point $(\alpha_{0}^{*},\alpha_{1}^{*})$ such that
the defender's benefit $\beta_{0}(\alpha_{0},\alpha_{1}^{*}) $is maximized at $\alpha_{0}= \alpha_{0}^{*}$ and the attacker's benefit
$\beta_{1}(\alpha_{0}^{*},\alpha_{1}) $ is maximized at $\alpha_{1}= \alpha_{1}^{*}$ .
To begin with, some useful notation. We denote by opt0($\alpha_{1}$) the set of values (rates
of play $\alpha_{0}$) that optimize the benefit of the defender for a fixed rate of play $\alpha_{1}$ of the
attacker. Similarly, we denote by opt1($\alpha_{0}$) the set of values (rates of play $\alpha_{1}$) that optimize
the benefit of the attacker for a fixed rate of play $\alpha_{0}$ of the defender. The following
theorem specifies Nash equilibria for the periodic game and is proven in Appendix A. \\
\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.4]{Images/bestresp.png}
\caption{This figure shows the three subcategories of each case. 'A' stands for Case 2.A: $\delta_{D} \geq d+\delta_{A} \geq \delta_{A}$ and 'B' stands for Case 2.B: $d+\delta_{A} \geq \delta_{D} \geq  \delta_{A} $ }
\label{grafiekbestr}
\end{figure}

@@

Nash equilibria are points with the property that neither player benefits by deviating in isolation from the equilibrium. We can compute Nash Equilibria for the periodic game as an intersection point of curves $opt_{D}$ and $opt_{A}$. To determine $opt_{D}(\alpha_{A})$ we need to compute the derivative of  $\beta_{D}(\alpha_{D},\alpha_{A}) $ for a fixed $\alpha_{A}$. We consider two cases:\\

\subsection*{Case 1: $\delta_{D} \leq \delta_{A} $}
The benefit formula obtained in the previous chapter for this case is as follows:
\begin{equation*}
\beta_{D}(\delta_{D},\delta_{A}) = 1 - \dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{D}}{\delta_{D}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}} + \dfrac{d}{\delta_{A}}
\end{equation*}
If we take the partial derivative for a fixed $\delta_{A}$ we get the following result:
\begin{equation*}\label{formdelta}
\frac{\partial \beta_{D}(\delta_{D},\delta_{A})}{\partial \delta_{D}} = - \dfrac{1}{2\delta_{A}} + \dfrac{k_{D}}{\delta_{D}^{2}} + \dfrac{d^{2}}{2\delta_{D}^{2}\delta_{A}}
\end{equation*}

The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{D}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{D} = \sqrt{2\delta_{A}k_{D} + d^{2}}
\end{equation*}

This leads to the following deduction given the sign of the coefficient of $\delta_{D}^{2}$: The function increases on $[0, \sqrt{2\delta_{A}k_{D} + d^{2}}]$ and is decreasing on $[\sqrt{2\delta_{A}k_{D} + d^{2}}, \infty]$. So we have a maximum at $\delta_{D} = min \{ \delta_{A}, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $. Taking the minimum of the two values is needed because $\delta_{D}$ cannot be larger than $\delta_{A}$. \\
~~\\

@@

The benefit formula obtained in the previous chapter for this case is as follows:
\begin{equation*}
\beta_{D}(\delta_{D},\delta_{A})= \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} = \dfrac{\delta_{A} + 2 (d-k_{D})}{\delta_{D}}
\end{equation*}

Given that $\delta_{D}$ is always positive, the benefit function can be either positive or negative depending on the numerator of the above fraction. For $\delta_{A} + 2(d-k_{D}) > 0$ the benefit will be always positive but decreasing, see figure \ref{ShapeUp}. \\
The defender will play if $ \delta_{A} > 2(k_{D} -d)$ and $k_{D} > d$. The defender will not play if $k_{D} < d$ because then $ \delta_{A}$ is negative.\\
\begin{figure}
\centering
\includegraphics[scale=0.5]{Images/ShapesUp.png} 
\caption{The benefit function is of the shape of 1/x if $\delta_{D}$ is always positive and if $\delta_{A} + 2(d-k_{D}) > 0$. }
\label{ShapeUp}
\end{figure}

For $\delta_{A} + 2(d-k_{D}) < 0$, the benefit will always be negative so the defender will not play. See figure \ref{ShapeDown}. This is independent of the value of $k_{D}$ and $ d$.

\begin{figure}
\centering
\includegraphics[scale=0.5]{Images/ShapeDown.png} 
\caption{The benefit function is of the shape of -1/x if $\delta_{D}$ is always positive and if $\delta_{A} + 2(d-k_{D}) < 0$.}
\label{ShapeDown}
\end{figure}
%The derivative of the above formula for a fixed $\delta_{A}$ results in the following:
%\begin{equation*}
%\frac{\partial \beta_{D}(\delta_{D},\delta_{A})}{\partial \delta_{D}} = -\dfrac{\delta_{A}}{2\delta_{D}^{2}} - \dfrac{d}{\delta_{D}^{2}} + \dfrac{k_{D}}{\delta_{D}^{2}}
%\end{equation*}
%The obtain the stationary points the first derivative is set equal to zero and the roots of the resulting equation are found:
%\begin{equation*}
%\frac{\partial \beta_{D}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{A} = 2(k_{D}-d) = dk_{D} - 2d
%\end{equation*}
%
This leads to the following deduction:
\begin{description}
\item If $k_{D} \leq d$ 
\begin{description}
\item decreasing $ \delta_{A} < 2(k_{D} -d)$, $ \delta_{A}$ is negative
\item increasing  $\delta_{A} > 2(k_{D} -d)$ 
\end{description}
\item If $k_{D} > d$ 
\begin{description}
\item increasing $ \delta_{A} < 2(k_{D} -d)$
\item decreasing  $\delta_{A} > 2(k_{D} -d)$ 
\end{description}
\end{description}
~~\\

@@

The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\dfrac{\beta_{D}(\alpha_{D},\alpha_{A})}{\partial \delta_{D}} = \dfrac{\delta_{A}}{2\delta_{D}} + \dfrac{d}{\delta_{D}} - \dfrac{k_{D}}{\delta_{D}} - \dfrac{(d-(\delta_{D} - \delta_{A}))^{2}}{2\delta_{D}\delta_{A}}
\end{equation*}

The derivative of the above formula for a fixed $\delta_{A}$ results in the following:
\begin{equation*}
\frac{\partial \beta_{D}(\alpha_{D},\alpha_{A})}{\partial \delta_{D}} =  - \dfrac{1}{2\delta_{D}} + \dfrac{k_{D}}{\delta_{D}^{2}} + \dfrac{d^{2}}{2\delta_{D}^{2}\delta_{A}}
\end{equation*}

@@

\begin{equation*}
\frac{\partial \beta_{D}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{D} = \sqrt{2\delta_{A}k_{D} + d^{2}}
\end{equation*}

This leads to the following deduction: The function increases on $[0, \sqrt{2\delta_{A}k_{D} + d^{2}}]$ and is decreasing on $[\sqrt{2\delta_{A}k_{D} + d^{2}}, \infty]$. So there is a maximum on $\delta_{D} = minimum \{ \delta_{A}, \sqrt{2\delta_{A}k_{D} + d^{2}} \} $ \\

@@

The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =\dfrac{\delta_{D}}{2\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} - \dfrac{d}{\delta_{A}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ 2k_{A} = \dfrac{(\delta_{D}-d)^{2}}{\delta_{D}}
\end{equation*}

@@

\subsection*{Case 2.A: $\delta_{D} \geq d+\delta_{A} \geq \delta_{A} $ }
The benefit formula obtained previously for this case is as follows:
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) =1- \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{k_{A}}{\delta_{A}} - \dfrac{d}{\delta_{D}}
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = \dfrac{-1}{2\delta_{D}} + \dfrac{k_{A}}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ \delta_{A} = \sqrt{2\delta_{D}k_{A}}
\end{equation*}
it follows that $\beta_{A}(\delta_{D},\cdot)$ is increasing on $[0,\sqrt{2k_{A}\delta_{D}}]$ and decreasing on $[\sqrt{2k_{A}\delta_{D}}, \infty]$ and thus has a maximum on $\delta_{A} = maximum \{\delta_{D}, \sqrt{2k_{A}\delta_{D}} \} $. The maximum between $\delta_{D}$ and $ \sqrt{2k_{A}\delta_{D}}$ is needed because $\delta_{A} $ cannot exceed $\delta_{D}$ in this case. \\

@@

The benefit formula obtained previously for this case is as follows: 
\begin{equation*}
\beta_{A}(\delta_{D},\delta_{A}) = 1 - \dfrac{\delta_{A}}{2\delta_{D}} - \dfrac{d}{\delta_{A}} - \dfrac{k_{A}}{\delta_{A}} + \dfrac{(d-(\delta_{D}-\delta_{A})^{2}}{2\delta_{D}\delta_{A}} 
\end{equation*}
The derivative for a fixed $\delta_{D}$ is as follows:
\begin{equation*}
\dfrac{\partial \beta_{A}(\delta_{D},\delta_{A})}{\partial \delta_{A}} = -\dfrac{\delta_{D}}{2\delta_{A}^{2}} + \dfrac{k_{A}}{\delta_{A}^{2}} - \dfrac{d^{2}}{2\delta_{D}\delta_{A}^{2}} + \dfrac{d}{\delta_{A}^{2}}
\end{equation*}
The stationary points (maximum, minimum) can be found by setting the first derivative equal to zero and finding the roots of the resulting equation:
\begin{equation*}
\frac{\partial \beta_{A}(\alpha_{D},\alpha_{A})}{\partial \delta_{D}} =0 ~~~~~~ =>~~~~~~ 2k_{A} = \dfrac{(\delta_{D}-d)^{2}}{\delta_{D}}
\end{equation*}

@@

This brings us to the following opt function for : \todo{juiste resultaten hier nog invullen}
From this analyses we can compute $opt_{D}(\delta_{A})$ for two different cases as:
 \begin{displaymath}
  opt_{D}(\delta_{A}) = \left\{
     \begin{array}{lr}
       0, & \delta_{A} < 2(k_{D} - d)\\
       0, & \delta_{A} = 2(k_{D} - d) \\
       \sqrt{d^{2} + 2\delta_{A}k_{D}}, & \delta_{A} > 2(k_{D} - d)
     \end{array}
   \right.
\end{displaymath}

\todo{ kA met kD vergelijken en nash evenwichten vinden}
\todo{ een voorbeeld invullen met specifieke waarden}
